---
title: "Authentication"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{authentication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
cookies_png <- "cookies.png"
```

There are two ways to authentication: an automated one which gives you anonymous cookies and a manual one which gives you user cookies.
`traktok` uses these cookies to make request appear as they come from your ordinary browser.
However, since some request require a logged in user, the respective functions need cookies from an authenticated user.

## Anonymous cookies

Authentication happens automatically the first time you run a function.
If you want to do this explicitly, use this function:

```{r}
tt_get_cookies()
```

It will guide you through the process.
If you want to create multiple cookie files, you can use the `name` argument:

```{r}
tt_get_cookies(name = "cookies_new")
```


## Logged in user

Pyktok uses the module [browser_cookie3](https://github.com/borisbabic/browser_cookie3) to directly access the cookies saved in your browser.
Such an infrastructure does not exists, to my knowledge, in `R` (tell me if I'm wrong!).
Instead, you can export the necessary cookies from your browser using a browser extension (after logging in at TikTok.com at least once).
I can recommend ["Get cookies.txt"](https://chrome.google.com/webstore/detail/get-cookiestxt-locally/cclelndahbckbenkjhflpdbgdldlbecc) for Chromium based browsers or ["cookies.txt"](https://addons.mozilla.org/en-US/firefox/addon/cookies-txt/) for Firefox.

`r knitr::include_graphics(cookies_png)`

Once you've saved this file, you read it into `traktok`, which will store it permanently.

```{r}
tt_get_cookies(x = "tiktok.com_cookies.txt")
```

If you want to create multiple cookie files, you can use the `name` argument:

```{r}
tt_get_cookies(x = "tiktok.com_cookies.txt", name = "cookies_new")
```


## Multiple cookie files

`tt_get_cookies` will save a cookie file in the location returned by `tools::R_user_dir("traktok", "config")`.
Set `save = FALSE` if you want to prevent this.
Using `options(tt_cookiefile = "some\path")`, you can change the default location.
If you have, for example, multiple cookie files in the default location:

```{r}
options(tt_cookiefile = file.path(tools::R_user_dir("traktok", "config"), paste0(cookies_new, ".rds")))
```

Alternatively, you can also set cookies for every function:

```{r}
cookie_files <- list.files(tools::R_user_dir("traktok", "config"), full.names = TRUE)
tt_videos(video_urls = "https://www.tiktok.com/@tiktok/video/6584647400055377158?is_copy_url=1&is_from_webapp=v1",
          cookiefile = cookie_files[1])
tt_videos(video_urls = "https://www.tiktok.com/@tiktok/video/6584647400055377158?is_copy_url=1&is_from_webapp=v1",
          cookiefile = cookie_files[2])
```

If you ever run into problems due to an expired cookie, you might want to delete the files in the default folder to get a fresh start.
